Zero-Shot Task Adaptation by Homoiconic Meta-mapping (HoMM)

### 2019-12-06 writing/poster/HoMM_transferable_skills_poster.tex
Some conclusions

\begin{block}{\huge Experiments}
\vspace{-0.5em}
\begin{columns}
\begin{column}[t]{0.48\textwidth}
\textbf{Polynomial regression:}
\begin{itemize}
\item Basic tasks: regress polynomials (degree \(\leq 3\)) in 4 variables from examples. 
\item Meta-mappings: transform polynomial by permuting variables, adding or multiplying constants, squaring. 
\item Good zero-shot performance!
\end{itemize}
\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{../figures/poly/meta_results.png}
\end{figure}
\end{column}
\begin{column}[t]{0.48\textwidth}
\textbf{Simple card games:}
\begin{itemize}
\item Basic tasks: input is hand, make bet, get stochastic reward. A variety of games with different rules. 
\item Meta-mappings: transform game by trying to lose, changing values of suits. 
\item Good zero-shot performance!
\end{itemize}
\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{../figures/meta_mapping.png}
\end{figure}
\end{column}
\end{columns}
\end{block}
\end{column}

\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Why \& prior work}
\begin{itemize}
\item Prior work has considered zero-shot task performance from language descriptions, with approaches that implicitly use prior task knowlege for the novel task.
\item However, transforming a task representation provides a richer and more explicit way to use prior knowledge.
\item Probably because of this, meta-mapping offers better zero-shot performance than a baseline of performing the task from natural language alone.
\item Meta-mapping thus offers a happy intermediate between meta-learning (which requires data on the new task), and zero-shot performance from language alone.
\end{itemize}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{../figures/why_meta_mapping.png}
\label{fig_why_meta_mapping}
\end{figure}

\end{block}
\begin{block}{\huge Conclusions}
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}

>>>>

\begin{block}{\huge Experiments}
\vspace{-0.5em}
\begin{columns}
\begin{column}[t]{0.48\textwidth}
\textbf{Polynomial regression:}
\begin{itemize}
\item Basic tasks: regress polynomials (degree \(\leq 3\)) in 4 variables from examples. 
\item Meta-mappings: transform polynomial by permuting variables, adding or multiplying constants, squaring. 
\item Good zero-shot performance!
\end{itemize}
\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{../figures/poly/meta_results.png}
\end{figure}
\end{column}
\begin{column}[t]{0.48\textwidth}
\textbf{Simple card games:}
\begin{itemize}
\item Basic tasks: input is hand, make bet, get stochastic reward. A variety of games with different rules. 
\item Meta-mappings: transform game by trying to lose, changing values of suits. 
\item Good performance in different hold-out conditions!
\end{itemize}
\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{../figures/meta_mapping.png}
\end{figure}
\end{column}
\end{columns}
\end{block}
\end{column}

\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Why \& prior work}
\vspace{-0.6em}
\begin{itemize}
\item Prior work has considered zero-shot task performance from language descriptions, with approaches that implicitly use prior task knowlege for the novel task.
\item Other prior work has considered using prior task similarity, but not transformation-based approaches.
\item However, transforming a task representation provides a richer and more explicit way to use prior knowledge.
\item Probably because of this, meta-mapping offers better zero-shot performance than a baseline of performing the task from natural language alone.
\item Meta-mapping thus offers a happy intermediate between meta-learning (which requires data on the new task), and zero-shot performance from language alone.
\end{itemize}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{../figures/why_meta_mapping.png}
\label{fig_why_meta_mapping}
\end{figure}

\end{block}
\begin{block}{\huge Conclusions}
\vspace{-0.6em}
\begin{itemize}
\item We propose \emph{meta-mappings}, a new perspective on zero-shot task performance via transformation of prior tasks. 
\item We propose homoiconic meta-mapping architectures as a parsimonious implementation that exploits the analogy between meta-mappings and basic tasks. 
\item We demonstrate the success of our approach, and show it outperforms a zero-shot baseline based on language descriptions alone. 
\item Check out our paper for additional studies, including:
    \begin{itemize}
    \Large
    \item Cueing meta-mappings from language.
    \item Lesions and baselines, like an unshared \(Z\) or a non-hyper-network based approach. 
    \item Applications to continual learning.
    \end{itemize}
\end{itemize}
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}
